Effects of resonant and random excitations on the proton beam in the Large Hadron Collider with applications to active halo control with pulsed hollow electron lenses

### 2018-09-16 response.tex

\section*{Report of Referee A}

\bco
The paper describes quite extensive simulation and experimental work 
in estimating the effects of either resonant or random dipole 
excitations on the LHC proton beam at injection. Quantities studied 
include beam loss, transverse beam profiles, and bunch length. The 
studies are motivated by the planned use of a hollow electron lens in 
the HL-LHC in pulsed mode (either resonantly with the betatron tune, 
or randomly). The pulsed mode should deplete the beam halo but not 
affect the beam core.

The paper is well written, with an excellent introduction, high 
quality tables and figure (a few issues are mentioned below), and very 
few typos. It reports in substantial detail on work performed in~2016 
and~2017.

My main criticism is with the discussion and conclusion. In this 
section, the previous sections are summarized as one would expect, but 
the authors may be able to come to more pronounced conclusions. The 
following sentence is somewhat disappointing after such a large body 
of work: ``However, further work is needed to identify, both in 
simulations and experimentally, candidate excitation patterns that are 
effective for halo removal and that preserve the beam core ...''. 
\eco

\bre We agree that the sentence may sound too weak. We wanted to
stress that this work focuses on core effects, and further studies are
needed on halo removal. The sentence was reworded to emphasize the
conclusions of these studies.  \ere

\bco
Would it be possible, for example, to summarize the beam losses of all
cases studied experimentally and in simulation in a single table? What
conclusions could be drawn from such a direct comparison for the cases
studied? Are any of these excitation pattern viable for a hollow
electron lens in the HL-LHC --- which was the motivation for this work
after all?
\eco

\note{Giulio, Miriam}

\bco
Typos and minor comments:

### 2018-09-16 resex.tex
Started responses to Referee A.

For active halo control in HL-LHC, resonant pulsing of the electron
lenses, or the addition of a random noise component to continuous
operation, may significantly extend the achievable range of halo
removal rates. However, further work is needed to identify, both in
simulations and experimentally, candidate excitation patterns that are
effective for halo removal and that preserve the beam core (such as
\eighthtp\ in these studies). Because of the complex dynamics,
tolerances on residual kicks vary widely, from a few nanoradians for
the most powerful (such as random at full strength or \seventhtp) to
about a hundred nanoradians for the more benign (such as
\eighthtp). The magnitude of the acceptable kicks depends on the
excitation pattern, on machine lattice, and on the type of application
(fast scraping before collisions vs.\ long-term tail suppression
during the course of a physics fill, for instance). Of course,
sensitivity to the experimental conditions may make resonant patterns
less attractive than a small random noise component added to a
constant kick.

>>>>

For active halo control in HL-LHC, resonant pulsing of the electron
lenses, or the addition of a random noise component to continuous
operation, may significantly extend the achievable range of halo
removal rates.  In these studies, we identified candidate excitation
patterns (such as \eighthtp) that preserve the beam core, and their
effects were quantified. As mentioned above, complementary
calculations and experiments are needed to evaluate their efficacy for
halo removal. Because of the complex dynamics, tolerances on residual
kicks vary widely, from a few nanoradians for the most powerful (such
as random at full strength or \seventhtp) to about a hundred
nanoradians for the more benign (such as \eighthtp). The magnitude of
the acceptable kicks depends on the excitation pattern, on machine
lattice, and on the type of application (fast scraping before
collisions vs.\ long-term tail suppression during the course of a
physics fill, for instance). Of course, sensitivity to the
experimental conditions may make resonant patterns less attractive
than a small random noise component added to a constant kick.
